### 2024-03-07 paper/main.tex
Fix typo

\begin{figure}[htbp]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/abs_performance-N.png}
        \caption{Absolute runtime with $P = 2^{10}$.}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/abs_performance-pP.png}
        \caption{Absolute runtime with $N = 2^{10}$.}
    \end{subfigure}\\
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/rel_performance-N.png}
        \caption{Relative improvement with $P = 2^{10}$.}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/rel_performance-pP.png}
        \caption{Relative improvement with $N = 2^{10}$.}
    \end{subfigure}
    \caption{Comparison of four different implementations of the Fast Fr\'echet Distance algorithm on a laptop (CPU: i7-11800H, GPU: GeForce RTX 3080 Mobile (16\,GB VRAM), CUDA Version: 12.2) using 32-bit floating point numbers. \textit{Vanilla} and \textit{Linear} refer to Alg.~\ref{alg:no_recursion} and \ref{alg:linear}, respectively. The SIMD implementation uses a batch size of $B = 32$ (twice the size of a 512-bit register in order to improve the instruction level parallelism) and relies on the AVX-512 instruction set; the baseline implementation uses the same technique to calculate $\sum_{ij} d_{ij}$. The CUDA implementation uses a grid and block size of 128 and 64, respectively, that was measured to perform best for $N=2^{13}$ and $P=2^{10}$. All variants utilize only a single CPU core.}
    \label{fig:benchmark_laptop}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/abs_performance-N.png}
        \caption{Absolute runtime with $P = 2^{10}$.}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/abs_performance-pP.png}
        \caption{Absolute runtime with $N = 2^{10}$.}
    \end{subfigure}\\
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/rel_performance-N.png}
        \caption{Relative improvement with $P = 2^{10}$.}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=.8\textwidth]{img/laptop/rel_performance-pP.png}
        \caption{Relative improvement with $N = 2^{10}$.}
    \end{subfigure}
    \caption{Comparison of four different implementations of the Fast Fr\'echet Distance algorithm on a laptop (CPU: i7-11800H, GPU: NVIDIA GeForce RTX 3080 Mobile (16\,GB VRAM), CUDA Version: 12.2) using 32-bit floating point numbers. \textit{Vanilla} and \textit{Linear} refer to Alg.~\ref{alg:no_recursion} and \ref{alg:linear}, respectively. The SIMD implementation uses a batch size of $B = 32$ (twice the size of a 512-bit register in order to improve the instruction level parallelism) and relies on the AVX-512 instruction set; the baseline implementation uses the same technique to calculate $\sum_{ij} d_{ij}$. The CUDA implementation uses a grid and block size of 128 and 64, respectively, that was measured to perform best for $N=2^{13}$ and $P=2^{10}$. All variants utilize only a single CPU core.}
    \label{fig:benchmark_laptop}
\end{figure}
